%-------------------------
% Resume in Latex
% Author: M.O. Haque
% Based on Jake Gutierrez's Template: https://github.com/sb2nov/resume
% License: MIT
%------------------------

\documentclass[letterpaper,10.5pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% Uncomment the desired font option:
% \usepackage[sfdefault]{FiraSans} % sans-serif
% \usepackage[sfdefault]{roboto} % sans-serif
% \usepackage[sfdefault]{noto-sans} % sans-serif
% \usepackage[default]{sourcesanspro} % sans-serif
% \usepackage{CormorantGaramond} % serif
% \usepackage{charter} % serif

% Page layout settings
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.75in}
\addtolength{\evensidemargin}{-0.75in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-.75in}
\addtolength{\textheight}{1.5in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\small
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\footnotesize{
    {#1} % Removed \vspace here
  }
}

\newenvironment{tightitemize}
  {\begin{itemize}[left=0pt, label={}, itemsep=0pt, topsep=0pt, partopsep=0pt, parsep=0pt]}
  {\end{itemize}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & {\small #2} \\
      \textit{\footnotesize#3} & \textit{\footnotesize #4} \\
    \end{tabular*}\vspace{-7pt} % Reduce spacing after the subheading
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\footnotesize#1} & \textit{\footnotesize #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \footnotesize#1 & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-3pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.1in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-3pt}}

\newcommand{\resumeEducationEntry}[4]{
  \item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{\small #1} & \textit{\footnotesize #2} \\
    \textit{\footnotesize#3} & \textit{\footnotesize #4} \\
  \end{tabular*}\vspace{-5pt}
}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape M.O. Haque} \\ \vspace{1pt}
    \footnotesize QA Engineer | 5 Years+ Experience $|$ \href{mailto:Secure.at3137312055@gmail.com}{\underline{E-mail: Secure.at3137312055@gmail.com}} $|$ 
    Phone: 313-731-2055 \\
    US Citizen | Orlando, FL $|$ 
    \href{https://www.LinkedIn.com/in/secure-at-whitehat}{\underline{LinkedIn: secure-at-whitehat}} $|$
    \href{https://github.com/oscpprep}{\underline{GitHub: oscpprep.github.io / Global-Aid.github.io}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
  \resumeSubHeadingListStart
    \resumeItem{I'm a QA Automation Engineer passionate about simplifying complex testing processes. I focus on developing and running automated tests to ensure software and systems function as intended. I enjoy exploring creative approaches to enhance testing and thrive in collaborative environments where we work together to solve challenges and build great products.}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Work History}
  \resumeSubHeadingListStart
\resumeSubheading
  {Sineris}{March 2023 – Present, Orlando, FL}
  {QA Automation Tester Consultant}{}
  \resumeItemListStart
  \resumeItem{Designed and implemented test plans, performing smoke and regression tests for CRM software.}
  \resumeItem{Developed automated test scripts using WebdriverIO with Cucumber BDD and Selenium WebDriver.}
  \resumeItem{Executed security, performance, and mobile compatibility tests; tested integrations with external systems.}
  \resumeItem{Created and maintained feature files covering extensive UI elements, navigation, and workflows.}
  \resumeItem{Collaborated with developers to identify and resolve issues, enhancing system stability and reliability.}
  \resumeItemListEnd

\resumeSubheading
  {BA Soft Tech}{Dec 2023 – June 2024, Orlando, FL}
  {QA Automation Engineer}{}
  \resumeItemListStart
  \resumeItem{Developed automated test scripts using Python, Selenium, and Capybara.}
  \resumeItem{Conducted API testing for RESTful services and automated Android application testing with Espresso.}
  \resumeItem{Created and maintained test scripts with WebdriverIO and Cucumber BDD; enhanced Cypress test automation.}
  \resumeItem{Integrated test scripts with TestRail and built interactive consoles for WebdriverIO development.}
  \resumeItem{Configured Jenkins for CI/CD, improving build and deployment efficiency by 30\%.}
  \resumeItemListEnd

\resumeSubheading
  {Quantum IT Services}{Feb 2021 – Dec 2023, New York, NY}
  {Security Analyst Intern}{}
  \resumeItemListStart
  \resumeItem{Monitored and analyzed real-time alerts using SIEM tools; responded to security incidents and collaborated with incident response teams.}
  \resumeItem{Managed and tuned security tools (antivirus, IDS/IPS, firewalls) to enhance threat detection and reduce false positives.}
  \resumeItem{Conducted vulnerability assessments, prioritized patches, and integrated threat intelligence into daily operations.}
  \resumeItem{Performed detailed analysis of security logs, leveraged forensics tools for incident investigations, and contributed to security awareness programs.}
  \resumeItemListEnd

\resumeSubheading
  {IIE Inc}{Aug 2019 – Jun 2023, Elgin, IL}
  {Network Security Engineer Intern}{}
  \resumeItemListStart
  \resumeItem{Utilized threat investigation frameworks and applied MITRE resources for Cyber Threat Intelligence.}
  \resumeItem{Conducted threat analysis using Yara, OpenCTI, and managed the MISP Threat Sharing Platform.}
  \resumeItem{Performed memory and disk forensics, executed malware analysis, and developed infrastructure hunting methodologies.}
  \resumeItem{Engaged in threat emulation, phishing defense, and buffer overflow exploitation; proficient in real-time threat detection with Snort and Zeek.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education / Certification}
  \resumeSubHeadingListStart
    \resumeEducationEntry{Microsoft Administrative Associate}{2023 – 2024}{New Horizons of NE Florida, Jacksonville, FL USA}{}
    \resumeEducationEntry{CompTIA Security+ CE Certification}{Issued Jul 2022 - Expires Jul 2025}{Credential ID: a9080fea-d1d4-4b12-b7ab-0e65488759be}{}
    \resumeEducationEntry{Master of Arts/Science in Religious and Social Sciences}{2014 – 2020}{IIE.inc, Elgin, IL USA}{}
  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills \& Toolsets}
\resumeSubHeadingListStart
\resumeSubheading{QA Test Automation \& Development}{}{}{}
\begin{tightitemize}
  \resumeItem{Languages: Python (Selenium, Appium), JavaScript, Selenium, Ruby (Capybara)}
  \resumeItem{Test Frameworks: WebDriverIO, Cypress, JUnit, BDD: Cucumber}
  \resumeItem{Database: CRUD operations with SQL in MongoDB}
  \resumeItem{Version Control: Git, GitHub, Bitbucket; CI/CD: Jenkins, GitLab CI/CD, CircleCI}
  \resumeItem{Test Management: Jira, Azure Boards, TestRail, Tools: Docker, Postman, Allure, Selenium Grid, Sauce Labs}
\end{tightitemize}

\resumeSubheading{Penetration Testing \& Exploitation}{}{}{}
\begin{tightitemize}
  \resumeItem{Tools: Aircrack-ng, BeEF, Burp Suite, Hydra, John the Ripper, Metasploit, Sqlmap, Wireshark, Nikto, Nmap, Recon-ng, Gobuster}
\end{tightitemize}

\resumeSubheading{Cyber Defense}{}{}{}
\begin{tightitemize}
  \resumeItem{Endpoint Monitoring: Osquery, Wazuh; Firewalls: pfSense, FortiGate}
  \resumeItem{Network Monitoring: Splunk, Zeek, Snort, ELK Stack; OSINT: SpiderFoot, Shodan, Google Dorks, Maltego}
\end{tightitemize}

\resumeSubheading{Threat Intelligence \& Incident Response}{}{}{}
\begin{tightitemize}
  \resumeItem{Threat Intel: MISP, OpenCTI, MITRE ATT\&CK, ThreatConnect; Incident Response: Cyber Kill Chain, Pyramid of Pain, Unified Kill Chain, NIST}
  \resumeItem{Forensics: Memory leaks, Disk (Autopsy, FTK Imager); Malware Analysis: Yara}
\end{tightitemize}

\resumeSubHeadingListEnd

\end{document}
